An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 Revision/response.tex

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions. The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set. The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.3: \textcolor{blue}{
	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image. On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS. Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space. The performance is similar to that of the single-modal dataset in Figure 4. This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query. In contrast, the Text2image dataset shown in Figure 9 is different. The query set and the base dataset belong to two completely different modalities. Queries are far from the dataset points, and the ground truths are more dispersed. To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance." 
}

Section 4.3.3:\textcolor{blue}{
		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
}

### 2025-07-31 Revision/response.tex

\noindent
\textbf{Response:} 
Thank you for your suggestion. We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. For more details, please refer to our response Meta R6.

%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:} 
%Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
Thank you for pointing this out. The original reference [49], now updated to reference [45], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms. We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques. We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version. To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}

 \textcolor{blue}{"
% 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}

@@

\textbf{Regarding index partitioning and merging:}

For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them. However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction. Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization. However, in our experiments, we did not enable quantization in any of our experiments. Therefore, no quantization time was included in the reported index build times.

\textbf{Regarding the exclusion of Vamana in Figure 7 (now Figure 6):}

We appreciate the observation of reviewer. Figure 6 presents experiments on multi-attribute construction and search, using Boolean AND logic. The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included. Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space. (\textbf{Please see the "Multi-Attribute Construction and Multi-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.})

### 2025-07-31 Revision/response.tex

\textcolor{blue}{
	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
}
%%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%

\myfbox{
	\begin{metarevision}
		\textit{Evaluate if the server setting affects the relative ordering of methods in experiments}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
That is a great suggestion. In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors. \textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}

Section 4.2.3:
%\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b. Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 10. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values."}

Section 4.3.3:
%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b. When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results."}
\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 15. Our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results."}

@@

\noindent
\textbf{Response:} 
Thank you for your suggestion. We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. For more details, please refer to our response Meta R6.

%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:} 
%Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
Thank you for pointing this out. The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms. We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques. We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version. To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}

 \textcolor{blue}{"
% 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
 	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications."}

@@

\textbf{Regarding index partitioning and merging:}

For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them. However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction. Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization. However, in our experiments, we did not enable quantization in any of our experiments. Therefore, no quantization time was included in the reported index build times.

\textbf{Regarding Figure 7 and the exclusion of Vamana:}

We appreciate the observation of reviewer. Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic. The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included. Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space. (\textbf{Please see the "Multi-Attribute Construction and Multi-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.})

### 2025-07-31 Revision/response.tex

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions. The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set. The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.3: \textcolor{blue}{
	"	We conduct experiments on two multi-modal datasets Text2image-Mix and Text2image. 
	%This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
	On Text2image-Mix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
	Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space. The performance is similar to that of the single-modal dataset in Figure 4. This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query. In contrast, the Text2image dataset shown in Figure 9 is different. The query set and the base dataset belong to two completely different modalities. Queries are far from the dataset points, and the ground truths are more dispersed. To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance."
}

Section 4.3.3:\textcolor{blue}{
		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because these range query algorithms most are  graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
}

### 2025-07-31 Revision/response.tex

Section 4.3.3:
%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b. When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results."}
\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 12b. Our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results."}

%%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.. At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets. The results are shown in Figure~\ref{fig:recall-latency}:
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
	\label{fig:recall-latency}
\end{figure}

### 2025-07-31 Revision/response.tex

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions. The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set. The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.3: \textcolor{blue}{
	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image. On Text2imageMix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS. Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space. The performance is similar to that of the single-modal dataset in Figure 4. This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality. This is not actually a difficult query. In contrast, the Text2image dataset shown in Figure 9 is different. The query set and the base dataset belong to two completely different modalities. Queries are far from the dataset points, and the ground truths are more dispersed. To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance." 
}

Section 4.3.3:\textcolor{blue}{
		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
}

### 2025-07-31 Revision/response.tex

%For range filtering, please see section 4.3.1.
 %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 Section 4.3.1:
\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend. As we analyzed in the section on attribute filtering."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}

Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low. StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation. CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}

Section 4.3.3:
\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}

### 2025-07-31 Revision/response.tex

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions. The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set. The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.3: \textcolor{blue}{
	"We conduct experiments on the Text2image-Mix dataset. This dataset contains image and text vectors and is a hybrid multi-modal dataset. As shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS. Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly. In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality. Therefore, the performance on this dataset is similar to the results shown in Figure 4. In contrast, the Text2image dataset shown in Figure 9 is different. The query set and the base dataset belong to two completely different modalities. Queries are far from the dataset points, and the ground truths are more dispersed. To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance." 
}

Section 4.3.3:\textcolor{blue}{
		"Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
}

@@

	\caption{Comparison of Real and Synthetic Attributes}
	\label{fig:range_2_2}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Instead of using the point ID, run experiments with meaningful attributes for RF-NN search on datasets (Deep, YT-Audio, WIT).}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations. To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes. As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible. The key factor remains the size of the query range. \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}

@@

\textcolor{blue}{"Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. "}

In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion. We added more detailed and in-depth analysis to provide a clearer explanation. \textbf{(Please see the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}

	\textcolor{blue}{
	"ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets. This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost. SeRF, another HNSW-based method, also exhibits very short construction time. During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}

\textcolor{blue}{
	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node. This design introduces redundant computation and high construction cost. However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}

@@

\textcolor{blue}{
	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead. Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}

%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.

### 2025-07-31 Revision/response.tex

Section 4.2.3:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level. This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}

Section 4.3.3:
\textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB). At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios. Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB"}

%%%%%%%%%%%%%%%%%%%%%% R9 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer insights and guidelines wrt the strength and weaknesses of the compared system.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
%Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
%
%To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
Thank you very much for your insightful comments. We fully agree with your views. We have revised the discussion section of the paper accordingly. In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions. Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
\textbf{(Please see Section 5.1.1, Section 5.1.2 and Section 5.1.3, highlighted in blue in the revised manuscript.)}

Section 5.1.1:\textcolor{blue}{
	"Overall, UNG, NHQ and FilteredDisk-ANN demonstrate strong performance. However, UNG suffers from performance degradation when the attribute count differs between indexing and querying. NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution. }

\textcolor{blue}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries. FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios. However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution. In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}

\textcolor{blue}{
	CAPS, based on clustering, features low index space overhead. It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
	Puck is well-suited for large-scale datasets such as those with 100 million points. It offers fast index construction and low memory consumption in such scenarios. "}

@@

Section 5.1.2: \textcolor{blue}{
	"WinFilter achieves the best search performance but requires high time and memory resources during index construction. For large-scale datasets (e.g., with 100 million points), parameter tuning—particularly of tree height—is needed to prevent excessive index growth. When QPS and recall are not strict requirements, its basic variant, Vamana-WST, offers a more efficient alternative with significantly lower indexing overhead.
}

\textcolor{blue}{
	iRange has relatively low time and space costs for index construction. However, its search performance declines significantly with increasing query range. Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.}

\textcolor{blue}{
	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios. It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution."}

@@

Senction 5.1.3:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}

\textcolor{blue}{
	ACORN demonstrates average overall performance. Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

\textcolor{blue}{
	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects."}
%下面放那个优劣势表

### 2025-07-31 VLDB2026/main.tex

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
	\textcolor{blue}{
		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because these range query algorithms most are  graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}. As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets.
		}

>>>>

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
	\textcolor{blue}{
		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}. As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets.
		}
